\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-14 paper/paper.tex
remove dup background sections
Formatting
Implementation pass

\section{Background}

\input{background.tex}
% 1 page
Background on TLS and Refraction Networking

@@

\section{Implementation}
In order to scale up to 10Gbps and beyond,
one has to utilize multiple cores and employ load balancing.
We use PF\_RING built-in load balancer \it{zbalance} to efficiently
distribute load between 4 cores.
Our timeout is based on last IP address usage time, which prevents us from
balancing load based on source IP address,
as censor would be able to observe
same destination IP address picking or not picking up
depending on source IP address.
To avoid such unusual behavior we balance on destination IP.
Since PF\_RING does not feature load balancing based only on destination
IP address, we made a custom implementation of this zbalance policy.

@@

-Language choice (Rust, Go, minimal C)
-Open source (client, station and application)

>>>>

\input{background.tex}

@@

\section{Implementation}

We implemented the Dark Decoy protocol and tested it in a 10~Gbps ISP testbed
with real traffic. Similar to TapDance~\cite{tapdance}, we used PF\_RING to
consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) dark decoy's address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

\FigImplementation

\subsection{Detector}

Our detector is a modified fork of the open source TapDance
implementation~\cite{tapdance-source}.
We implemented our detector in approximately 1,800 lines of Rust (compared to
over 5,000 lines for TapDance)\footnote{excluding (from both) about 3,000 lines
of auto-generated protobuf code}.

We used PF\_RING to load balance the 10~Gbps link over 4~CPU cores. PF\_RING
supports balancing across cores based on flow (5-tuple) or source and
destination IPs. However, both of these options present challenges for our Dark
Decoy detector. One issue is that registrations could be processed on a
different core than the packets sent to that specific dark decoy address. For
instance, a client could have its registration handled by Core 1, while its
packets to the dark decoy address end up on Core 3, which doesn't know about the
original registration.

To address this, we used Redis~\cite{redis} to allow each process to announce
(publish) newly registered decoys to the other cores so they can
add them to their local list of registered dark decoy addresses.
However, this introduces two new problems. First, a core might add a
registration \emph{after} it has already received and processed packets destined
for the specified dark decoy. This typically isn't a problem when running on a
single core, as packets are processed sequentially. Second, each core may
timeout each dark decoy at different times, potentially leading to differing
behavior that is visible to a censor. For instance, if we used the
source/destination IPs to load balance, a censor's packets to a dark decoy could
be processed by a different core than the client. If the censor waits for the
known timeout before sending a probe, its core may have timed out that dark
decoy, while the client's core has refreshed the timeout of the dark decoy due
to active use.

To address the first issue, we force the client to delay sending its connection
to the dark decoy until a short time after registration. In practice, we force
the client to wait until the registration decoy responds before starting a
connection with the registered dark decoy.

To address the second issue, we implemented a new load-balancing algorithm in
PF\_RING to select the core based solely on the destination IP address of the
packet. This still means we must use Redis to tell all of the cores of new
registrations, but that only one core will be responsible for processing all of
the packets sent to a given dark decoy, regardless of who or when it is sent.

\subsection{Application}

We implemented our application in about 500~lines of Golang. Though we note
other protocols (e.g. obfsproxy or WebRTC) could be used as the application, we
implemented a mask site mimicking application, that pretends to be a mask site
when actively probed by the censor.

The application accepts connections to dark decoy addresses forwarded by the
detector and rewritten to the local address using \texttt{iptables}.
The application also receives out-of-band information about registrations from the
detector via a ZMQ~\cite{zmq} connection, which informs the application of the
registering client's IP address, the secret seed, and other configuration
information passed by the client.

Once the application accepts a connection, it initially acts as a transparent
proxy to the mask site specified by the client during registration. The
application parses the handshake, forwarding packets back and forth between
client and mask site without modification, and extracting the server and client
randoms. The application attempts to decrypt the first application data record
from the client using a key derived from the secret seed, and client and server
randoms. We use the uTLS library~\cite{utls} on both the application and client
to allow us to change the TLS secrets being used after the handshake.

If the decryption is successful, the application switches to forwarding
(decrypted) data back and forth with a client-specified endpoint, such as a
SOCKS proxy, which can multiplex multiple client connections over the single
connection to the dark decoy.

\subsection{Client}

Our client is also written in Golang, and uses a TapDance-like protocol for
registration. We note that this protocol should be harder for censors to observe
because it consists of only a single (complete) request, and the station does
not have to spoof packets as the decoy used during registration, only passively
observe them.

After registering, the client connects to the derived dark decoy address, and
switches secrets after the handshake. At this point, a local application (e.g.
SOCKS client) can connect to the client, and it will transparently be connected to
the remote end via the encrypted dark decoy connection.

\if0
In order to scale up to 10Gbps and beyond,
one has to utilize multiple cores and employ load balancing.
We use PF\_RING built-in load balancer \emph{zbalance} to efficiently
distribute load between 4 cores.
Our timeout is based on last IP address usage time, which prevents us from
balancing load based on source IP address,
as censor would be able to observe
same destination IP address picking or not picking up
depending on source IP address.
To avoid such unusual behavior we balance on destination IP.
Since PF\_RING does not feature load balancing based only on destination
IP address, we made a custom implementation of this zbalance policy.

@@

-Language choice (Rust, Go, minimal C)
-Open source (client, station and application)
\fi
